Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
BCP: wording

The {\tt testpack}\footnote{%
http://hackage.haskell.org/package/testpack}
package provides a combinator to expect exceptions,
similar to {\tt shouldThrow} from
Section~\ref{sec:expacting-exceptions}:

>>>>

The {\tt testpack} package provides a combinator to expect exceptions,
similar to {\tt shouldThrow} from
Section~\ref{sec:expacting-exceptions}:
